gavin_thesis_R

### 2024-10-11 notebooks/gavin_thesis_markdown.qmd
Submission to Pediatric Research

Figure 3.1
```{r}
#| echo = FALSE
label = sigfunc(SSSChi.t$p.value)
m1 <- ggwithinstats(
  data = comp_CCV_chi,
  x = Method,
  y = Chi,
  ylab = "Chi (ppm)",
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid")) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_CCV_chi$Chi)*1.05), size=4, label = label)

label = sigfunc(SSSSvO2.t$p.value)
m2 <- ggwithinstats( 
  data = comp_SSS_chi,
  x = Method,
  y = Measured.Susceptibility, 
  ylab = "Chi (ppm)",
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid")) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_SSS_chi$Measured.Susceptibility)*1.05), size=4, label = label )

label = sigfunc(CCVChi.t$p.value)
m3 <- ggwithinstats(
  data = comp_CCV_SvO2,
  x = Method,
  y = Oxygen.Saturation,
  ylab = "SvO2 (%)",
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid") ) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_CCV_SvO2$Oxygen.Saturation)*1.05), size=4, label = label )

label = sigfunc(CCVSvO2.t$p.value)
m4 <- ggwithinstats(
  data = comp_SSS_SvO2,
  x = Method,
  y = Oxygen.Saturation,
  ylab = "SvO2 (%)",
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid") ) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_SSS_SvO2$Oxygen.Saturation)*1.05), size=4, label = label )
(patch1 <- (m1 + m2)/(m3 + m4) + 
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 10)))
```

```{r}
#| label: fig-methodplot
#| fig-width: 8
#| fig-height: 5
#| fig-cap: "Vein-specific susceptibility and oxygen saturation values by method. (A, B) contains violin plots comparing subject χ (ppm) acquired from QSM (A) and its paramagnetic component (B); (C, D) contains violin plots comparing subject SvO2 (%) acquired from QSM (C) and its paramagnetic component (D). Raw data points from paramagnetic maps are shown as filled green circles and raw data points from QSM are shown as filled orange circles. Each line connects the raw data points of a single subject. (***) indicates P<0.05."
patch1
```

@@

label = sigfunc(RegionQSMChi.t$p.value)
 p1 <- ggwithinstats(
  data = comp_legit_starfsl,
  x = Vein,
  y = Chi,
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "Chi (ppm)",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#D95F02")) + 
  ggplot2::annotate("text", x=1.5, y=(max(comp_legit_starfsl$Chi)*1.05), size=4, label = label)

label = sigfunc(RegionQSMSvO2.t$p.value)
p2 <- ggwithinstats(
  data = comp_SSS_IntVein_CSvO2,
  x = Vein,
  y = CSvO2,
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "SvO2 (%)",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#D95F02")
) + 
  ggplot2::annotate("text", x=1.5, y=(max(comp_SSS_IntVein_CSvO2$CSvO2)*1.05), size=4, label = label)

label = sigfunc(RegionChisepChi.t$p.value)
p3 <- ggwithinstats(                     #boxplot of chi comparison between regions
  data = comp_chisep_chi,
  x = Vein,
  y = Chi, 
  results.subtitle = FALSE,
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "Chi (ppm)",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#1B9E77")
) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_chisep_chi$Chi))*1.05, size=4, label = label)

label = sigfunc(RegionChisepSvO2.t$p.value)
p4 <- ggwithinstats(                    #boxplot of svo2 comparison between regions
  data = comp_chisep_CSvO2,
  x = Vein,
  y = CSvO2, 
  results.subtitle = FALSE,
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "SvO2 (%)",
  type = "nonparametric",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#1B9E77")
) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_chisep_CSvO2$CSvO2)*1.05), size=4, label = label)

@@

```{r}
#| label: fig-regionplot
#| fig-width: 8
#| fig-height: 5
#| fig-cap: "Inter-venous comparisons of susceptibility and oxygen saturation. Violin plots comparing (A, C) χ (ppm) and (B, D) SvO2 (%) between the CCV and the SSS. Panels (A) and (B) used data acquired from QSM, and its raw data points are shown as filled orange circles. Panels (C) and (D) used data acquired from paramagnetic maps, and its raw data points are shown as filled green circles. Each line connects the raw data points of a single subject. (***) indicates p<0.05; (n.s.) indicates no significant difference."
patch2
```

>>>>

Figure 3.1
```{r}
#| echo = FALSE
label = sigfunc(SSSChi.t$p.value)
m1 <- ggwithinstats(
  data = comp_CCV_chi,
  x = Method,
  y = Chi,
  title = "Cerebral Central Veins",
  ylab = "Chi (ppm)",
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid")) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_CCV_chi$Chi)*1.05), size=4, label = label)

label = sigfunc(SSSSvO2.t$p.value)
m2 <- ggwithinstats( 
  data = comp_SSS_chi,
  x = Method,
  y = Measured.Susceptibility, 
  title = "Superior Sagittal Sinus",
  ylab = "Chi (ppm)",
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid")) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_SSS_chi$Measured.Susceptibility)*1.05), size=4, label = label )

label = sigfunc(CCVChi.t$p.value)
m3 <- ggwithinstats(
  data = comp_CCV_SvO2,
  x = Method,
  y = Oxygen.Saturation,
  title = "Cerebral Central Veins",
  ylab = "SvO2 (%)",
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid") ) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_CCV_SvO2$Oxygen.Saturation)*1.05), size=4, label = label )

label = sigfunc(CCVSvO2.t$p.value)
m4 <- ggwithinstats(
  data = comp_SSS_SvO2,
  x = Method,
  y = Oxygen.Saturation,
  title = "Superior Sagittal Sinus",
  ylab = "SvO2 (%)",
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid") ) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_SSS_SvO2$Oxygen.Saturation)*1.05), size=4, label = label )
(patch1 <- (m1 + m2)/(m3 + m4) + 
  plot_annotation(tag_levels = 'A') & 
  theme(plot.tag = element_text(size = 10)))
```

```{r}
#| label: fig-methodplot
#| fig-width: 8
#| fig-height: 5
#| fig-cap: "**Vein-specific susceptibility and oxygen saturation values by method.** (A, B) contains violin plots comparing subject chi (ppm) acquired from the cerebral central veins; (C, D) contains violin plots comparing subject SvO2 (%) acquired from the superior sagittal sinus. Raw data points from paramagnetic maps are shown as filled green circles and raw data points from QSM are shown as filled orange circles. Each line connects the raw data points of a single subject. (***) indicates P<0.05."
patch1
```

@@

label = sigfunc(RegionQSMChi.t$p.value)
 p1 <- ggwithinstats(
  data = comp_legit_starfsl,
  x = Vein,
  y = Chi,
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "Chi (ppm)",
  title = "QSM",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#D95F02")) + 
  ggplot2::annotate("text", x=1.5, y=(max(comp_legit_starfsl$Chi)*1.05), size=4, label = label)

label = sigfunc(RegionQSMSvO2.t$p.value)
p2 <- ggwithinstats(
  data = comp_SSS_IntVein_CSvO2,
  x = Vein,
  y = CSvO2,
  title = "QSM",
  results.subtitle = FALSE,
  type = "p",
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "SvO2 (%)",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#D95F02")
) + 
  ggplot2::annotate("text", x=1.5, y=(max(comp_SSS_IntVein_CSvO2$CSvO2)*1.05), size=4, label = label)

label = sigfunc(RegionChisepChi.t$p.value)
p3 <- ggwithinstats(                     #boxplot of chi comparison between regions
  data = comp_chisep_chi,
  x = Vein,
  y = Chi, 
  title = "Paramagnetic susceptibility",
  results.subtitle = FALSE,
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "Chi (ppm)",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#1B9E77")
) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_chisep_chi$Chi))*1.05, size=4, label = label)

label = sigfunc(RegionChisepSvO2.t$p.value)
p4 <- ggwithinstats(                    #boxplot of svo2 comparison between regions
  data = comp_chisep_CSvO2,
  x = Vein,
  y = CSvO2, 
  title = "Paramagnetic susceptibility",
  results.subtitle = FALSE,
  pairwise.display = "all",
  bf.message = FALSE,
  xlab = "Region",
  ylab = "SvO2 (%)",
  type = "nonparametric",
  centrality.plotting = FALSE,
  point.path.args = list(linewidth = 0.25, linetype = "solid"),
  point.args = list(color = "#1B9E77")
) +
  ggplot2::annotate("text", x=1.5, y=(max(comp_chisep_CSvO2$CSvO2)*1.05), size=4, label = label)

@@

```{r}
#| label: fig-regionplot
#| fig-width: 8
#| fig-height: 5
#| fig-cap: "**Inter-venous comparisons of susceptibility and oxygen saturation**. Violin plots comparing (A, C) chi (ppm) and (B, D) SvO2 (%) between the CCV and the SSS. Panels (A) and (B) used data acquired from QSM, and its raw data points are shown as filled orange circles. Panels (C) and (D) used data acquired from paramagnetic maps, and its raw data points are shown as filled green circles. Each line connects the raw data points of a single subject. (***) indicates p<0.05; (n.s.) indicates no significant difference."
patch2
```
